%-------------------------
% Resume in Latex
% Author : Vinayak Suresh Chandavar
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{fontawesome}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Vinayak Suresh Chandavar} % Your Name
\newcommand{\course}{Electronics and Communication Engineering} % Your Program
\newcommand{\phone}{+91-7619225588} % Your Phone Number
\newcommand{\emailb}{vinayakchandavar4@gmail.com} %Email 2

\begin{document}
\fontfamily{cmr}\selectfont

\parbox{\dimexpr\linewidth\relax}{
\begin{tabularx}{\linewidth}{L r} \\
  \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ \phone}\\
  \course &  \href{mailto:\emailb}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emailb}}\\
  {Bachelor of Engineering} &  \href{https://github.com/vinayakec69}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}} \\
  {Sahyadri College of Engineering and Management, Mangaluru} & \href{https://www.linkedin.com/in/vinayak-chandavar-b1a81732b}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
\end{tabularx}
}

%-----------------TECHNICAL SKILLS--------------

\section{\textbf{Technical Skills and Interests}}
 \begin{itemize}[leftmargin = 0.05in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, Bash, JavaScript, TypeScript.} \\
     \textbf{AI \& Computer Vision}{: Ultralytics YOLOv8, PyTorch, OpenCV, TensorFlow.js.} \\
     \textbf{Hardware \& Edge-AI}{: NVIDIA Jetson Orin Nano, Intel RealSense Depth Cameras, ESP32.} \\
     \textbf{Web Development \& Cloud}{: React 18, Firebase (Firestore, RTDB), Tailwind CSS, Vite.} \\
     \textbf{Areas of Interest}{: Edge-AI Deployment, Computer Vision, Autonomous Systems.} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------EDUCATION-----------
\section{\textbf{Education}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sahyadri College of Engineering and Management, Mangaluru} {}
      {Bachelor of Engineering in Electronics and Communication Engineering}{2027}
    \resumeSubheading
      {Shri Marikamba Government PU College, Sirsi}{}
      {Pre-University Course (Class 12) -- Dept. of PUE, Karnataka}{}
    \resumeSubheading
      {Government Marigudi High School, Sirsi}{}
      {Secondary School Certificate (Class 10) -- KSEEB}{}
  \resumeSubHeadingListEnd
\vspace{-5.5mm}


%-----------PROJECTS-----------------
\section{\textbf{Projects}}
\resumeSubHeadingListStart

    \resumeProject
      {SmartSeg: Edge-AI Based Plastic Waste Sorting System \href{https://github.com/vinayakec69/CV-MODEL-IN-Material-Recovery-Facility}{\faGithub} \href{https://drive.google.com/drive/folders/1Zn13gNGXuI9A54_cFm94XNbU1lvjyUoC}{\faFilePdf}} 
      {Real-time CV system on Jetson Orin Nano to automate MRF conveyor belt sorting at 30+ FPS.} 
      {Emphasis Lab} 

      \resumeItemListStart
        \item {Technologies used: YOLOv8, OpenCV, Python, Intel RealSense, Headless Linux.}
        \item {Engineered a zero-domain-gap dataset and a lightweight depth-gating algorithm to bypass GPU memory limits and prevent thermal throttling on edge hardware.}
        \item {Implemented a 7/10 multi-frame supermajority rolling buffer to eliminate single-frame classification hallucinations.}
    \resumeItemListEnd

    \vspace{0mm}
    
     \resumeProject
      {KRUX: AI-Powered Gamified Smart Bin Ecosystem \href{https://krux1-mig.vercel.app/}{\faExternalLink} \href{https://drive.google.com/drive/folders/1p1tOm34N03Xj3UcDNOdZdAIGQ9hUQ7Fm}{\faFilePdf}} 
      {A full-stack hardware/software ecosystem gamifying recycling to prevent contamination.} 
      {} 

      \resumeItemListStart
        \item {Technologies used: React 18, Tailwind, Firebase (RTDB, Firestore), TensorFlow.js, ESP32.}
        \item{Built a Progressive Web App (PWA) with on-device ML inference in the browser, ensuring 100\% user privacy and zero cloud inference costs.}
        \item{Interfaced the web app with an ESP32 hardware bin using Firebase RTDB to achieve a seamless, zero-latency sensor handshake for fraud detection.}
    \resumeItemListEnd

    \vspace{0mm}

    \resumeProject
      {CareLens: Vision AI Wearable for the Visually Impaired \href{https://drive.google.com/drive/folders/11CVru8caBQXr3PiLs4WtGNFv-dSNB-pq}{\faFilePdf}} 
      {Wearable assistive tech providing 3D semantic understanding and audio navigation cues.} 
      {} 

      \resumeItemListStart
        \item {Technologies used: PyTorch, YOLOv8, Intel RealSense, pyttsx3, Jetson Orin Nano.}
        \item{Fine-tuned PyTorch models for offline indoor obstacle detection, heavily optimizing dataloader constraints (batch=1) to prevent `CUDACachingAllocator` OOM crashes.}
        \item{Designed a low-latency offline audio engine using `pyttsx3` and a Type-C DAC to bypass Bluetooth bottlenecks and deliver conversational audio warnings.}
    \resumeItemListEnd

    \vspace{0mm}

  \resumeSubHeadingListEnd
\vspace{-5.5mm}


%-----------EXPERIENCE/RESEARCH-----------------
\section{\textbf{Experience \& Research}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Emphasis Lab, SCEM}{Adyar, Mangaluru}
      {Project Developer / AI Researcher}{2023 - Present}
      \vspace{-2.0mm}
      \resumeItemListStart
    \item {Developed and deployed real-time Edge-AI solutions utilizing NVIDIA Jetson hardware and depth-sensing technology.}
    \item {Specialized in resolving low-level Linux memory constraints (`nvlm assert` bugs) to maximize deep learning inference on embedded systems.}
    \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-8.5mm}

%-----------ACHIEVEMENTS / HACKATHONS-----------------
\section{\textbf{Achievements \& Hackathons}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Hackathon Participant \& Finalist: }
    {Various National \& State Level Hackathons. \href{https://drive.google.com/drive/folders/1JoRxXEXK24WbS0SCnmrWko8Q4e-QyX0Y}{\faExternalLink}}
    {\textbf{2023 - 2024}}
\resumeSubHeadingListEnd
\vspace{-5mm}

\setlength{\footskip}{4.08003pt}
\end{document}
